Viscous Transport in Eroding Porous Media

### 2019-10-02 docs/transport/erosion_transport.tex
NM

Next, we use the streamlines to compute the tortuosity and the anomalous
dispersion rate\nick{s} of eroding geometries.  To achieve statistical
convergence, we use $N_p = 1000$ streamlines~\cite{bel-sal-rin1992}. To
compute the tortuosity, we require the velocity at the inlet $x=-1$.
These normalized velocities are plotted in
Figure~\ref{fig:Eroding20tort}(a) for the eroded geometry at porosity
$\phi = 62.9\%$ (Figure~\ref{fig:Eroding20tort}(c)).  The velocities are
similar to the work of Matyka et al.~\cite{mat-kha-koz2008} (see Figure
4(a)), except that our cross-section, by construction, does not cut
through any of the grains.  Next, in Figure~\ref{fig:Eroding20tort}(b),
we plot the local tortuosity~\eqref{eqn:localTort} by calculating the
relative length of each streamline as it traverses the channel from
$x=-1$ to $x=1$.  The local tortuosity ranges from 1 to 1.27, meaning
that one of the streamlines is 27\% longer than it would have been if
the grains were absent.  The average streamline is 9.79\% longer
\nick{\st{than if the grains had been absent}, \st{so the} or equivalently the tortuosity of the \st{eroded channel} geometry is $1.098$}.  Again, comparing the local tortuosity to
Matyka~\cite{mat-kha-koz2008} (Figure 4(b)), the results are
qualitatively similar. However, since our initial cross-section does not
cut through the grains, the local tortuosity does not have any gaps.
\nick{Discontinuities in local tortuosity \st{happens} occur} when nearby
streamlines diverge on opposite sides of a grain.  In
Figure~\ref{fig:Eroding20tort}(c), we plot the pairs of streamlines that
correspond to the ten largest jumps in the local tortuosity.
Corresponding pairs are plotted in the same color.

>>>>

Next, we use the streamlines to compute the tortuosity and the anomalous
dispersion rate\nick{s} of eroding geometries.  To achieve statistical
convergence, we use $N_p = 1000$ streamlines~\cite{bel-sal-rin1992}. To
compute the tortuosity, we require the velocity at the inlet $x=-1$.
These normalized velocities are plotted in
Figure~\ref{fig:Eroding20tort}(a) for the eroded geometry at porosity
$\phi = 62.9\%$ (Figure~\ref{fig:Eroding20tort}(c)).  The velocities are
similar to the work of Matyka et al.~\cite{mat-kha-koz2008} (see Figure
4(a)), except that our cross-section, by construction, does not cut
through any of the grains.  Next, in Figure~\ref{fig:Eroding20tort}(b),
we plot the local tortuosity~\eqref{eqn:localTort} by calculating the
relative length of each streamline as it traverses the channel from
$x=-1$ to $x=1$.  The local tortuosity ranges from 1 to 1.27, meaning
that one of the streamlines is 27\% longer than it would have been if
the grains were absent.  The average streamline is 9.79\% longer
\nick{\st{than if the grains had been absent}, \st{so the} or equivalently the tortuosity of the \st{eroded channel} geometry is $1.098$}.  Again, comparing the local tortuosity to
Matyka~\cite{mat-kha-koz2008} (Figure 4(b)), the results are
qualitatively similar. However, since our initial cross-section does not
cut through the grains, the local tortuosity does not have any gaps.
\nick{Discontinuities in local tortuosity \st{happens} occur} when nearby
streamlines diverge \nick{\st{on opposite sides of a grain} to circumvent a grain}.  In
Figure~\ref{fig:Eroding20tort}(c), we plot pairs of streamlines \nick{associate with the ten largest jumps in the local tortuosity, with each pair of corresponding streamlines plotted in the same color.}
